Using evolutionary algorithms to optimize the estimation of a diffusion process

### 2015-01-26 paperGecco.tex
Includes biblio and fixes LaTeX problems
References #4. Also rearranges tables. It has to be anonymyzed for double-blind review and also equations have to be checked so that they fit in the two-columns format. Please @nuriastatgirl or @mgarenas do it.

\usepackage{url}
\urldef{\mailsa}\path|{mgarenas,nrico,deromero,pacv,jmerelo}@ugr.es|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}
\conferenceinfo{GECCO'15,} {July 11-15, 2015, Madrid, Spain.}
    \CopyrightYear{2015}
    \crdata{TBA}
    \clubpenalty=10000
    \widowpenalty = 10000
\mainmatter  % start of an individual contribution
%

@@

\begin{figure}
  \centering
\begin{tabular}{ c c }
  \epsfig{file=graf1prueba.eps,width=.50\textwidth} & \epsfig{file=graf2prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-5}$ & $\sigma^2=10^{-4}$ \\
  \epsfig{file=graf3prueba.eps,width=.50\textwidth} & \epsfig{file=graf4prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-3}$ & $\sigma^2=10^{-2}$\\
\end{tabular}
\caption{\footnotesize{Simulated paths for Gompertz-lognormal process from $t_0=1$ to $t_{500}=100$, with values $m=1$, $\beta=0.2$, and $c=0.013$ and different values of noise; $\sigma^2=10^{-5}$, $\sigma^2=10^{-4}$, $\sigma^2=10^{-3}$ and  $\sigma^2=10^{-2}$. Black lines highlight the paths last value $x_{i;500}$ are maximum, minimum and the quartiles of the output range. }} \label{1:figura:path}
\end{figure}

@@

{\scriptsize
\begin{table}
\caption{\footnotesize{Average of the estimates $(\overline{\hat{m}}$, $\overline{\hat{\beta}}$, $\overline{\hat{c}}$, $\overline{\hat{\sigma}^{2}})$; standard deviation of each one ($sd$); average ans standard deviation of the value of function (\ref{ecuacion}) ($\overline{\hat{F}},sd$); best found solution (${\hat{F}}_{min}$). Paths simulated with $m=1$, $\beta=0.2$ and $c=0.013$ and $\sigma^2=\{10^{-5},10^{-4},10^{-3},10^{-2}\}$. For each method, the number of the successful solutions (\emph{Succ.}) has been included in the second column.}}
\begin{center}
{\scriptsize
\begin{tabular}{lc|rrrrrrrrrr}
   M & Succ.  & $\overline{\hat{m}}\quad$&$sd\qquad$ &  $\overline{\hat{\beta}}\quad$ &$sd\qquad$ &  $\overline{\hat{c}}\qquad$ &$sd\qquad$ &  $\overline{\hat{\sigma}^{2}}\quad\quad$ &$sd\qquad$& $\overline{\hat{F}}\qquad$  &$sd\qquad$ \\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-5}$} \\

\hline
IM 		& $1$ 	&$1,0076$&$-\qquad$      	    & $0,20034$&$-\qquad$      	&$0,01299$&$-\qquad$    	    &$10*10^{-6}$&$-\qquad$	&$-205013,0$	&$-\qquad$\\
NR		& $12$	&$1,0129$ & $7*10^{-10}$	& $0,20273$&$2*10^{-8}$	&$0,01319$ &$3*10^{-8}$	&$12*10^{-6}$&$7*10^{-11}$	&$-256494,2$	&$2*10^{-6}$	 \\
VNS  	& $30$  &$0,9972$&$1*10^{-2}$    & $0,20398$&$3*10^{-3}$  	&$0,01363$&$8*10^{-4}$  	&$14*10^{-6}$&$5*10^{-6}$	&$-254626,4$	&$2298,7$	 \\
SA 		& $30$  &$1,0129$&$3*10^{-5}$ 	& $0,20273$&$9*10^{-6}$  	&$0,01319$&$3*10^{-7}$ 	&$12*10^{-6}$&$4*10^{-8}$	&$-256494,0$	&$1*10^{-1}$	 \\
EA 		& $30$  &$1,0129$&$2*10^{-4}$		& $0,20273$&$4*10^{-6}$  	&$0,01319$&$1*10^{-6}$ 	&$12*10^{-6}$&$4*10^{-9}$	&$-256494,2$	&$1*10^{-2}$\\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-4}$} \\
\hline
IM 		&$1$	&$1,0144$&$-\qquad$           & $0,19846$&$-\qquad$         &$0,01338$&$-\qquad$      &$10*10^{-5}$&$-\qquad$	& $-194477,8$&$-\qquad$			 \\
NR 	&$21$	&$1,0395$&$3*10^{-8}$     &  $0,20815$&$3*10^{-7}$  &$0,01354$&$4*10^{-7}$  &$12*10^{-5}$&$9*10^{-10}$	& $-199315,7$&$2*10^{-5}$\\
VNS		&$30$	&$0,9970$&$1*10^{-2}$     & $0,20854$&$3*10^{-3}$   &$0,01374$&$1*10^{-3}$  &$12*10^{-5}$&$7*10^{-6}$	& $-199170,7$&$216,6$\\
SA 		&$30$	&$1,0394$&$1*10^{-7}$     & $0,20815$&$1*10^{-5}$   &$0,01354$&$1*10^{-5}$	&$12*10^{-4}$&$7*10^{-8}$	& $-199315,7$&$1*10^{-3}$\\
EA 		&$30$	&$1,0395$&$1*10^{-7}$     & $0,20815$&$1*10^{-5}$   &$0,01354 $&$1*10^{-5}$ &$12*10^{-5}$&$7*10^{-8}$	& $-199315,7$&$8*10^{-4}$\\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-3}$} \\
\hline
IM 		&$1$ 	&$1,1366$	&$-\qquad$    	&$0,22761$	&$-\qquad$    	&$0,01478$	&$-\qquad$    	&$10*10^{-4}$&$-\qquad$	& $-88350,2$	&$-\qquad$\\
NR 	&$14$	&$1,1366$	&$2*10^{-8}$	&$0,22761$	&$9*10^{-8}$	&$0,01478$	&$9*10^{-8}$ 	&$12*10^{-4}$&$2*10^{-12}$	& $-141799,8 $	&$7*10^{-8}$\\
VNS 	&$30$	&$0,9989$	&$1*10^{-2}$	&$0,22737$	&$3*10^{-3}$	&$0,01459$	&$8*10^{-4}$	&$13*10^{-4}$&$1*10^{-5}$	& $-141790,6$	&$10,0$\\
SA 		&$30$	&$1,1366$	&$2*10^{-4}$	&$0,22759$	&$6*10^{-5}$	&$0,01476$	&$2*10^{-5}$ 	&$12*10^{-4}$&$6*10^{-7}$	& $-141799,8 $&$8*10^{-3}$\\
EA 		&$30$	&$1,1366$	&$3*10^{-6}$	&$0,22761$	&$8*10^{-7}$	&$0,01478$	&$1*10^{-7}$ 	&$12*10^{-4}$&$5*10^{-9}$	& $-141799,8$&$4*10^{-6}$\\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-2}$} \\
\hline
IM 		&$0$ 	&$-\quad$&$ -\qquad$    		&$-\quad$&$-\qquad$    			&$-\quad$&$ -\qquad$    			&$-\qquad$&$-\qquad$				 &$-\qquad$			&$-\qquad$		\\
NR 	&$16$	&$1,5472$&$2*10^{-7}$	&$0,32957$&$2*10^{-7}$	&$0,02079$&$2*10^{-6}$ 	&$12*10^{-3}$&$4*10^{-10}$	&$-84972,8$		&$2*10^{-8}$\\
VNS 	&$30$	&$0,9371$&$5*10^{-3}$	&$0,33014$&$2*10^{-3}$	&$0,02081$&$5*10^{-4}$   &$12*10^{-3}$&$4*10^{-5}$ 	&$-84972,3$		&$0.75$		\\
SA 		&$30$	&$1,1366$&$2*10^{-4}$	&$0,22759$&$6*10^{-5}$	&$0,01476$&$2*10^{-5}$ 	&$12*10^{-3}$&$4*10^{-5}$	&$-84965,0$		&$1*10^{-3}$ \\
EA 		&$30$	&$1,5391$&$2*10^{-3}$	&$0,32210$&$6*10^{-4}$	&$0,01560$&$3*10^{-6}$ 	&$12*10^{-3}$&$7*10^{-6}$	&$-84965,1$		&$1*10^{-3}$ \\
\hline
\end{tabular}}
\label{tabla:parametros}
\end{center}
\end{table}
}
\normalsize

@@

{\scriptsize
\begin{table}
\caption{\footnotesize{Estimated set of parameters, function (\ref{ecuacion}) it provides and error measurements.}}
\begin{center}
{\scriptsize
\begin{tabular}{c|rrrrr|rrrrr}
\hline
   M & $\hat{F}_{min}\ $ &  $\hat{m}_{F_{min}}$ &  $\hat{\beta}_{F_{min}}$ &  $\hat{c}_{F_{min}}$ & $\hat{\sigma}^{2}_{F_{min}}\ $&  MSE\hspace{0.2cm} &  MAE &  MAPE &  SMAPE & MRAE  \\

@@

	 		IM & $-205013$		&$1,008$	&$0,200$	&$0,013$	&$26*10^{-5}$	& $2858$	&$30,52$ 	&$2,10$	&$0,02$	&$39,85$	\\
	 		NR & $-256494$		&$1,013$	&$0,203$	&$0,013$ 	&$13*10^{-6}$ & $2785$	&$28,48$	&$1,87$	&$0,02$	&$32,17$	\\
            VNS & $-256476$		&$0,999$	&$0,203$	&$0,013$    &$13*10^{-6}$	& $14052$	&$94,33$ 	&$5,74$	&$0,06$	&$71,20$	\\
 			SA & $-256494$    	&$1,013$	&$0,203$	&$0,013$   	&$12*10^{-6}$	&$2791$		&$28,51$  &$1,87$	&$0,02$ &$32,18$	\\
 			EA& $-256494$   	&$1,013$	&$0,203$	&$0,013$	&$13*10^{-6}$ 	&$2785$		&$	28,48$	&$1,87$	&$0,02$	&$32,17$ 	\\
 \hline
\hline
&\multicolumn{10}{c}{Noise Level $ \sigma^2= 10^{-4}$} \\
%&\multicolumn{5}{|c||}{Non-trimmed}&\multicolumn{5}{c|}{Trimmed} \\
\hline
	 	    IM & $-148757$		&$1,017$	&$0,198$	&$0,013$	&$244*10^{-5}$	&$51123$ 	&$146,42$ 	&$10,70$ 	&$0,10$	&$129,92$	\\
	 	    NR& $-199316$		&$1,039$	&$0,208$	&$0,014$	&$12*10^{-5}$ &$25027$	&$87,14$	&$5,43$		&$0,05$	&$73,73$ 	\\
            VNS& $-199315$		&$0,999$	&$0,208$	&$0,014$	&$13*10^{-5}$	&$154407$ 	&$300,77$ 	&$17,88$ 	&$0,20$	&$232,38$	\\
 			SA& $-199316$		&$1,039$	&$0,208$	&$0,014$	&$12*10^{-5}$ 	&$25025	$	&$87,13	$	&$5,43$		&$0,05$	&$73,73$	\\
 			EA & $-199316$		&$1,039$	&$0,208$	&$0,014$	&$12*10^{-5}$	&$25027$	&$87,14$	&$5,43$		&$0,05$	&$73,73$	\\
\hline
\hline
&\multicolumn{10}{c}{Noise Level $ \sigma^2= 10^{-3}$} \\
%&\multicolumn{5}{|c||}{Non-trimmed}&\multicolumn{5}{c|}{Trimmed} \\
\hline
 			IM&$-88517$	&$1,035$	&$0,186$	&$0,022$	&$275*10^{-4}$ 	&$16443800$	&$2262,92$ 	&$146,54$	&$0,75$		&$725,20$	\\
 			NR&$-141800$	&$1,137$	&$0,228$	&$0,015$	&$13*10^{-4}$ &$341403$		&$267,03$	&$15,88$	&$0,16$		&$71,62$	\\
           VNS &$-141800$	&$0,999$	&$0,228$	&$0,015$	&$13*10^{-4}$	&$1461321$	&$867,30$ 	&$44,93$	&$0,60$		&$208,52$	\\
 			SA &$-141800$	&$1,136$	&$0,228$	&$0,015$	&$13*10^{-4}$	&$340903$		&$266,83$	&$15,88$	&$0,16$		&$71,60$	\\
 			EA &$-141800$	&$1,137$	&$0,228$	&$0,015$	&$13*10^{-4}$	&$341403$		&$267,03$	&$15,88$	&$0,16$		&$71,62$	\\
\hline
\hline
&\multicolumn{10}{c}{Noise Level $\sigma^2=  10^{-2}$} \\
%&\multicolumn{5}{|c||}{Non-trimmed}&\multicolumn{5}{c|}{Trimmed} \\
\hline
 			IM 	&$-\ \ \ $				& $-\ \ $ 		&$-\ \ $		&$-\ \ $		& $-\ \ \ \ \ $		& $-\ \ \ \ $		&$-\ \ \ $		&$-\ \ $		 &$-\ \,$		&$-\ \ \,$\\
 			NR&$-84973$	&$1,547$	&$0,330$	&$0,021$	&$12*10^{-3}$ &$5120383$			&$955,6$	&$79,18$	&$0,54$		& $139,8$	\\
            VNS&$-84973$	&$0,939$	&$0,330$	&$0,021$	&$12*10^{-3}$	&$9921164$	& $1785,9$ 	&$78,32$	&$1,34$		& $136,7$	\\
 			SA &$-84965$	&$1,540$	&$0,322$	&$0,016$	&$12*10^{-3}$	&$5642929$			&$1010,4$	&$62,19$	&$0,54$	&$108,9$	\\
 			EA &$-84965$	&$1,539$	&$0,322$	&$0,016$	&$12*10^{-3}$	&$5634217$		&$1009,3$	&$62,29$	&$0,53$	&$109,1$	\\
\hline
\end{tabular}
}
\label{tabla:errores}\end{center}
\end{table}
}

@@

%The authors would like to thank the FEDER of European Union for financial support via project ``Sistema de Informaci{\'o}n y Predicci{\'o}n de bajo coste y aut{\'o}nomo para conocer el Estado de las Carreteras en tiempo real mediante dispositivos distribuidos" (SIPEsCa) of the ``Programa Operativo FEDER de Andaluc\'{i}a 2007-2013". We also thank all Agency of Public Works of Andalusia Regional Government staff and researchers for their dedication and their professionalism. This work has been supported in part by project ANYSELF (TIN2011-28627-C04-02) and MICINN (Spain) MTM2011-28962.
%\begin{figure}
%\begin{center}
%\epsfig{file=sipesca_2.eps,width=4cm}
%\end{center}
%\end{figure}
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case

>>>>

\usepackage{url}
\urldef{\mailsa}\path|{mgarenas,nrico,deromero,pacv,jmerelo}@ugr.es|

\begin{document}
\conferenceinfo{GECCO'15,} {July 11-15, 2015, Madrid, Spain.}
    \CopyrightYear{2015}
    \crdata{TBA}
    \clubpenalty=10000
    \widowpenalty = 10000
%\mainmatter  % start of an individual contribution
%

@@

\begin{figure*}[htb]
  \centering
\begin{tabular}{ c c }
  \epsfig{file=graf1prueba.eps,width=.50\textwidth} & \epsfig{file=graf2prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-5}$ & $\sigma^2=10^{-4}$ \\
  \epsfig{file=graf3prueba.eps,width=.50\textwidth} & \epsfig{file=graf4prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-3}$ & $\sigma^2=10^{-2}$\\
\end{tabular}
\caption{Simulated paths for Gompertz-lognormal processes from $t_0=1$ to $t_{500}=100$, with values $m=1$, $\beta=0.2$, and $c=0.013$ and different values of noise; $\sigma^2=10^{-5}$, $\sigma^2=10^{-4}$, $\sigma^2=10^{-3}$ and  $\sigma^2=10^{-2}$. Black lines highlight the paths last value $x_{i;500}$ are maximum, minimum and the quartiles of the output range. } \label{1:figura:path}
\end{figure*}

@@

\begin{table*}
\caption{\footnotesize{Average of the estimates $(\overline{\hat{m}}$, $\overline{\hat{\beta}}$, $\overline{\hat{c}}$, $\overline{\hat{\sigma}^{2}})$; standard deviation of each one ($sd$); average ans standard deviation of the value of function (\ref{ecuacion}) ($\overline{\hat{F}},sd$); best found solution (${\hat{F}}_{min}$). Paths simulated with $m=1$, $\beta=0.2$ and $c=0.013$ and $\sigma^2=\{10^{-5},10^{-4},10^{-3},10^{-2}\}$. For each method, the number of the successful solutions (\emph{Succ.}) has been included in the second column.}}
\begin{center}
{\scriptsize
\begin{tabular}{lc|rrrrrrrrrr}
   M & Succ.  & $\overline{\hat{m}}\quad$&$sd\qquad$ &  $\overline{\hat{\beta}}\quad$ &$sd\qquad$ &  $\overline{\hat{c}}\qquad$ &$sd\qquad$ &  $\overline{\hat{\sigma}^{2}}\quad\quad$ &$sd\qquad$& $\overline{\hat{F}}\qquad$  &$sd\qquad$ \\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-5}$} \\

\hline
IM 		& $1$ 	&$1,0076$&$-\qquad$      	    & $0,20034$&$-\qquad$      	&$0,01299$&$-\qquad$    	    &$10*10^{-6}$&$-\qquad$	&$-205013,0$	&$-\qquad$\\
NR		& $12$	&$1,0129$ & $7*10^{-10}$	& $0,20273$&$2*10^{-8}$	&$0,01319$ &$3*10^{-8}$	&$12*10^{-6}$&$7*10^{-11}$	&$-256494,2$	&$2*10^{-6}$	 \\
VNS  	& $30$  &$0,9972$&$1*10^{-2}$    & $0,20398$&$3*10^{-3}$  	&$0,01363$&$8*10^{-4}$  	&$14*10^{-6}$&$5*10^{-6}$	&$-254626,4$	&$2298,7$	 \\
SA 		& $30$  &$1,0129$&$3*10^{-5}$ 	& $0,20273$&$9*10^{-6}$  	&$0,01319$&$3*10^{-7}$ 	&$12*10^{-6}$&$4*10^{-8}$	&$-256494,0$	&$1*10^{-1}$	 \\
EA 		& $30$  &$1,0129$&$2*10^{-4}$		& $0,20273$&$4*10^{-6}$  	&$0,01319$&$1*10^{-6}$ 	&$12*10^{-6}$&$4*10^{-9}$	&$-256494,2$	&$1*10^{-2}$\\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-4}$} \\
\hline
IM 		&$1$	&$1,0144$&$-\qquad$           & $0,19846$&$-\qquad$         &$0,01338$&$-\qquad$      &$10*10^{-5}$&$-\qquad$	& $-194477,8$&$-\qquad$			 \\
NR 	&$21$	&$1,0395$&$3*10^{-8}$     &  $0,20815$&$3*10^{-7}$  &$0,01354$&$4*10^{-7}$  &$12*10^{-5}$&$9*10^{-10}$	& $-199315,7$&$2*10^{-5}$\\
VNS		&$30$	&$0,9970$&$1*10^{-2}$     & $0,20854$&$3*10^{-3}$   &$0,01374$&$1*10^{-3}$  &$12*10^{-5}$&$7*10^{-6}$	& $-199170,7$&$216,6$\\
SA 		&$30$	&$1,0394$&$1*10^{-7}$     & $0,20815$&$1*10^{-5}$   &$0,01354$&$1*10^{-5}$	&$12*10^{-4}$&$7*10^{-8}$	& $-199315,7$&$1*10^{-3}$\\
EA 		&$30$	&$1,0395$&$1*10^{-7}$     & $0,20815$&$1*10^{-5}$   &$0,01354 $&$1*10^{-5}$ &$12*10^{-5}$&$7*10^{-8}$	& $-199315,7$&$8*10^{-4}$\\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-3}$} \\
\hline
IM 		&$1$ 	&$1,1366$	&$-\qquad$    	&$0,22761$	&$-\qquad$    	&$0,01478$	&$-\qquad$    	&$10*10^{-4}$&$-\qquad$	& $-88350,2$	&$-\qquad$\\
NR 	&$14$	&$1,1366$	&$2*10^{-8}$	&$0,22761$	&$9*10^{-8}$	&$0,01478$	&$9*10^{-8}$ 	&$12*10^{-4}$&$2*10^{-12}$	& $-141799,8 $	&$7*10^{-8}$\\
VNS 	&$30$	&$0,9989$	&$1*10^{-2}$	&$0,22737$	&$3*10^{-3}$	&$0,01459$	&$8*10^{-4}$	&$13*10^{-4}$&$1*10^{-5}$	& $-141790,6$	&$10,0$\\
SA 		&$30$	&$1,1366$	&$2*10^{-4}$	&$0,22759$	&$6*10^{-5}$	&$0,01476$	&$2*10^{-5}$ 	&$12*10^{-4}$&$6*10^{-7}$	& $-141799,8 $&$8*10^{-3}$\\
EA 		&$30$	&$1,1366$	&$3*10^{-6}$	&$0,22761$	&$8*10^{-7}$	&$0,01478$	&$1*10^{-7}$ 	&$12*10^{-4}$&$5*10^{-9}$	& $-141799,8$&$4*10^{-6}$\\
\hline
\multicolumn{12}{c}{Noise Level $\sigma^2=10^{-2}$} \\
\hline
IM 		&$0$ 	&$-\quad$&$ -\qquad$    		&$-\quad$&$-\qquad$    			&$-\quad$&$ -\qquad$    			&$-\qquad$&$-\qquad$				 &$-\qquad$			&$-\qquad$		\\
NR 	&$16$	&$1,5472$&$2*10^{-7}$	&$0,32957$&$2*10^{-7}$	&$0,02079$&$2*10^{-6}$ 	&$12*10^{-3}$&$4*10^{-10}$	&$-84972,8$		&$2*10^{-8}$\\
VNS 	&$30$	&$0,9371$&$5*10^{-3}$	&$0,33014$&$2*10^{-3}$	&$0,02081$&$5*10^{-4}$   &$12*10^{-3}$&$4*10^{-5}$ 	&$-84972,3$		&$0.75$		\\
SA 		&$30$	&$1,1366$&$2*10^{-4}$	&$0,22759$&$6*10^{-5}$	&$0,01476$&$2*10^{-5}$ 	&$12*10^{-3}$&$4*10^{-5}$	&$-84965,0$		&$1*10^{-3}$ \\
EA 		&$30$	&$1,5391$&$2*10^{-3}$	&$0,32210$&$6*10^{-4}$	&$0,01560$&$3*10^{-6}$ 	&$12*10^{-3}$&$7*10^{-6}$	&$-84965,1$		&$1*10^{-3}$ \\
\hline
\end{tabular}}
\label{tabla:parametros}
\end{center}
\end{table*}

@@

\begin{table*}
\caption{\footnotesize{Estimated set of parameters, function (\ref{ecuacion}) it provides and error measurements.}}
\begin{center}
{\scriptsize
\begin{tabular}{c|rrrrr|rrrrr}
\hline
   M & $\hat{F}_{min}\ $ &  $\hat{m}_{F_{min}}$ &  $\hat{\beta}_{F_{min}}$ &  $\hat{c}_{F_{min}}$ & $\hat{\sigma}^{2}_{F_{min}}\ $&  MSE\hspace{0.2cm} &  MAE &  MAPE &  SMAPE & MRAE  \\

@@

	 		IM & $-205013$		&$1,008$	&$0,200$	&$0,013$	&$26*10^{-5}$	& $2858$	&$30,52$ 	&$2,10$	&$0,02$	&$39,85$	\\
	 		NR & $-256494$		&$1,013$	&$0,203$	&$0,013$ 	&$13*10^{-6}$ & $2785$	&$28,48$	&$1,87$	&$0,02$	&$32,17$	\\
            VNS & $-256476$		&$0,999$	&$0,203$	&$0,013$    &$13*10^{-6}$	& $14052$	&$94,33$ 	&$5,74$	&$0,06$	&$71,20$	\\
 			SA & $-256494$    	&$1,013$	&$0,203$	&$0,013$   	&$12*10^{-6}$	&$2791$		&$28,51$  &$1,87$	&$0,02$ &$32,18$	\\
 			EA& $-256494$   	&$1,013$	&$0,203$	&$0,013$	&$13*10^{-6}$ 	&$2785$		&$	28,48$	&$1,87$	&$0,02$	&$32,17$ 	\\
 \hline
\hline
&\multicolumn{10}{c}{Noise Level $ \sigma^2= 10^{-4}$} \\
%&\multicolumn{5}{|c||}{Non-trimmed}&\multicolumn{5}{c|}{Trimmed} \\
\hline
	 	    IM & $-148757$		&$1,017$	&$0,198$	&$0,013$	&$244*10^{-5}$	&$51123$ 	&$146,42$ 	&$10,70$ 	&$0,10$	&$129,92$	\\
	 	    NR& $-199316$		&$1,039$	&$0,208$	&$0,014$	&$12*10^{-5}$ &$25027$	&$87,14$	&$5,43$		&$0,05$	&$73,73$ 	\\
            VNS& $-199315$		&$0,999$	&$0,208$	&$0,014$	&$13*10^{-5}$	&$154407$ 	&$300,77$ 	&$17,88$ 	&$0,20$	&$232,38$	\\
 			SA& $-199316$		&$1,039$	&$0,208$	&$0,014$	&$12*10^{-5}$ 	&$25025	$	&$87,13	$	&$5,43$		&$0,05$	&$73,73$	\\
 			EA & $-199316$		&$1,039$	&$0,208$	&$0,014$	&$12*10^{-5}$	&$25027$	&$87,14$	&$5,43$		&$0,05$	&$73,73$	\\
\hline
\hline
&\multicolumn{10}{c}{Noise Level $ \sigma^2= 10^{-3}$} \\
%&\multicolumn{5}{|c||}{Non-trimmed}&\multicolumn{5}{c|}{Trimmed} \\
\hline
 			IM&$-88517$	&$1,035$	&$0,186$	&$0,022$	&$275*10^{-4}$ 	&$16443800$	&$2262,92$ 	&$146,54$	&$0,75$		&$725,20$	\\
 			NR&$-141800$	&$1,137$	&$0,228$	&$0,015$	&$13*10^{-4}$ &$341403$		&$267,03$	&$15,88$	&$0,16$		&$71,62$	\\
           VNS &$-141800$	&$0,999$	&$0,228$	&$0,015$	&$13*10^{-4}$	&$1461321$	&$867,30$ 	&$44,93$	&$0,60$		&$208,52$	\\
 			SA &$-141800$	&$1,136$	&$0,228$	&$0,015$	&$13*10^{-4}$	&$340903$		&$266,83$	&$15,88$	&$0,16$		&$71,60$	\\
 			EA &$-141800$	&$1,137$	&$0,228$	&$0,015$	&$13*10^{-4}$	&$341403$		&$267,03$	&$15,88$	&$0,16$		&$71,62$	\\
\hline
\hline
&\multicolumn{10}{c}{Noise Level $\sigma^2=  10^{-2}$} \\
%&\multicolumn{5}{|c||}{Non-trimmed}&\multicolumn{5}{c|}{Trimmed} \\
\hline
 			IM 	&$-\ \ \ $				& $-\ \ $ 		&$-\ \ $		&$-\ \ $		& $-\ \ \ \ \ $		& $-\ \ \ \ $		&$-\ \ \ $		&$-\ \ $		 &$-\ \,$		&$-\ \ \,$\\
 			NR&$-84973$	&$1,547$	&$0,330$	&$0,021$	&$12*10^{-3}$ &$5120383$			&$955,6$	&$79,18$	&$0,54$		& $139,8$	\\
            VNS&$-84973$	&$0,939$	&$0,330$	&$0,021$	&$12*10^{-3}$	&$9921164$	& $1785,9$ 	&$78,32$	&$1,34$		& $136,7$	\\
 			SA &$-84965$	&$1,540$	&$0,322$	&$0,016$	&$12*10^{-3}$	&$5642929$			&$1010,4$	&$62,19$	&$0,54$	&$108,9$	\\
 			EA &$-84965$	&$1,539$	&$0,322$	&$0,016$	&$12*10^{-3}$	&$5634217$		&$1009,3$	&$62,29$	&$0,53$	&$109,1$	\\
\hline
\end{tabular}
}
\label{tabla:errores}\end{center}
\end{table*}

@@

%The authors would like to thank the FEDER of European Union for financial support via project ``Sistema de Informaci{\'o}n y Predicci{\'o}n de bajo coste y aut{\'o}nomo para conocer el Estado de las Carreteras en tiempo real mediante dispositivos distribuidos" (SIPEsCa) of the ``Programa Operativo FEDER de Andaluc\'{i}a 2007-2013". We also thank all Agency of Public Works of Andalusia Regional Government staff and researchers for their dedication and their professionalism. This work has been supported in part by project ANYSELF (TIN2011-28627-C04-02) and MICINN (Spain) MTM2011-28962.
%\begin{figure}
%\begin{center}
%\epsfig{file=sipesca_2.eps,width=4cm}
%\end{center}
%\end{figure}
\bibliographystyle{abbrv}
\begin{thebibliography}{10}

\bibitem{proceedingBol}
Guti{\'e}rrez, R., Rico, N., Rom{\'a}n, P., Romero, D., Torres, F.:
Un nuevo proceso de difusi{\'o}n para modelizar patrones de crecimiento mixto exponencial-Gompertz. XXX Congreso Nacional SEIO. Libro de Actas, pp. 1--15 (2007)

\bibitem{Gut07b}
Guti{\'e}rrez, R., Rom{\'a}n, P., Romero, D., Serrano, J.J. y Torres, F.:
A new Gompertz-type diffusion process with application to random growth. Math. Biosci. 208,147--165 (2007)

\bibitem{GutCy}
Guti{\'e}rrez, R., Rom{\'a}n, P., Romero, D. and Torres, F.:
Applications of the univariate lognormal diffusion process with exogenous factors in forecasting. {Cybernet Syst.} {34}(8),709--724 (2003)

\bibitem{Gut99} Guti{\'e}rrez, R., Rom{\'a}n, P. and Torres, F.:
Inference and first-passage-times for the lognormal diffusion process with exogenous factors: application to modelling
in economics. Appl. Soch. Model. Bus. {15},325-332 (1999)

\bibitem{SA}
Ingber, L.:
Simulated annealing: Practice versus theory. Mathl. Comput. Modelling, vol. 18(11), pp. 29--57 (1993)

\bibitem{Kirkpatrick83}
S. Kirkpatrick1, C. D. Gelatt Jr. M. P. Vecch:
Optimization by Simulated Annealing. Science Vol. 220 no. 4598 pp. 671-680 (1983)

\bibitem{Michalewicz96}
Zbigniew Michalewicz:
Heuristic methods for evolutionary computation techniques. J. Heuristics 1(2):177-206 (1996)

\bibitem{EA}
B{\"{a}}ck, T.:
Evolutionary algorithms in theory and practice, Oxford University Press (1996)

\bibitem{Kloeden}
Kloeden, P. E., Platen, E. y Schurz, H.:
Numerical solution of SDE through computer experiments, {Springer-Verlag} (1994)

\bibitem{Rao}
Rao, N. J., Borwankar, J. D. y Ramkrishna, D.:
Numerical solution of Ito integral equations. {SIAM Journal on Control and Optimization} {12}, 124--139 (1974)

\bibitem{error}
De Gooijer, J.G., Hyndman, R.J.:
25 Years of IIF Time Series Forecasting: A Selective Review. Tinbergen Institute Discussion Papers No. TI 05-068/4 . (2005)

\bibitem{GProp}
P. A. Castillo, J. Carpio, J. J. Merelo, V. Rivas, G. Romero, and A. Prieto:
Evolving Multilayer Perceptrons, Neural Processing Letters, vol. 12, no. 2, pp. 115--127, 2000.

\bibitem{GPropII}
S. Fahlman:
Faster-learning variations on back-propagation: An empirical study, in Proceedings of the 1988 Connection- ist models summer school. M. Kaufmann, 1988, pp. 38--51.

\bibitem{lognormal}
Log-normal Distributions across the Sciences: Keys and Clues
Article in Bioscience 51, No. 5, May 2001, 341-352.

\bibitem{blx}
Manuel Lozano, Francisco Herrera, Natalio Krasnogor, and Daniel Molina:
Real-coded memetic algorithms with crossover hill-climbing. Evol. Comput. 12, 3. Sep, 2004, 273-302.

\bibitem{VNS} Mladenovic, N. and Hansen, P.: Variable neighborhood search. {Computers and Operations Research} {24}, 1097--1100 (1997)

\end{thebibliography}
